---
title: "Sampling and Replication Uncertainty"
output: 
  flexdashboard::flex_dashboard:
      vertical_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)

library(tidyverse)
theme_set(theme_bw())
library(plotly)
library(Hmisc)

source('functions.R')
```

Inputs {.sidebar}
=====

Set the *experimental design* using the parameters below. This is what scientists can control. 

```{r}
numericInput('n', 'Sample size (per group)', 5)
numericInput('N', 'Number of replications', 2)
```

The parameters below determine the properties of the *population* (curly- and straight-haired people).  Scientists *don't* control these. 

The true, population-level difference in mean height (curly - straight) is 
**`r renderText(input$curly_mean - input$straight_mean)` cm**. 

```{r}
numericInput('curly_mean', 'curly_mean', 170)
numericInput('straight_mean', 'straight_mean', 160)
numericInput('curly_sd', 'curly_sd', 7)
numericInput('straight_sd', 'straight_sd', 7)
```


# One Study #

```{r}
actionButton('go_one', 'Run one study')
```

```{r}
one_study = eventReactive(input$go_one, 
                          draw_a_sample(input$n,
                                        input$curly_mean, 
                                        input$curly_sd,
                                        input$straight_mean,
                                        input$straight_sd))
# renderTable(one_study())
# renderPlotly(ggplotly(plot_a_sample(one_study())))
```

Values {data-width=200}
-----

```{r}
p_value = reactive(calculate_p_value(one_study()))
# renderText(p_value())
```

The p-value of the difference in mean heights is `r renderText(p_value())`. 

This difference **`r renderText(ifelse(p_value() < .05, 'is', 'is not'))`** statistically significant. 

```{r}
renderTable(one_study())
```

Plot {data-width=400}
-----
```{r}
renderPlotly(ggplotly(plot_a_sample(one_study())))
```




# Many Replications #

```{r}
actionButton('go_replications', 'Run many replications')
```

```{r}
replications = eventReactive(input$go_replications, 
                             replicate_N_times(input$N, 
                                               input$n,
                                               alpha = .05,
                                        input$curly_mean, 
                                        input$curly_sd,
                                        input$straight_mean,
                                        input$straight_sd))
```

Plots {.tabset data-width=900}
-----

### Plot the first replication
```{r}
##<!-- plot_a_sample(replications$sample[[1]]) -->
renderPlotly(ggplotly(plot_a_sample(replications()$sample[[1]])))
```

### Distribution of "curly greater"
<!-- curly_greater_plot(replications) -->
```{r}
renderPlotly(ggplotly(curly_greater_plot(replications())))
```

### Distribution of statistical significance
<!-- stat_sig_plot(replications) -->
```{r}
renderPlotly(ggplotly(stat_sig_plot(replications())))
```

### Distribution of p-values
<!-- p_value_plot(replications) -->
```{r}
renderPlotly(ggplotly(p_value_plot(replications())))
```

### Volcano plot {data-padding=40}
```{r}
checkboxInput('pub_bias', 'Publication bias')
```

```{r}
renderPlotly(ggplotly(volcano_plot(replications(), 
                                  publication_bias = input$pub_bias))) 
```

Padding {data-width=100}
-----
