---
title: "Sampling and Replication Uncertainty"
output: 
  flexdashboard::flex_dashboard:
      horizontal_layout: scroll
runtime: shiny
---

```{r setup, include=FALSE}
library(flexdashboard)

library(tidyverse)
theme_set(theme_bw())
library(plotly)
library(Hmisc)

source('functions.R')

plot_width = 500
plot_height = 3/4*plot_width
```

Inputs {.sidebar}
=====

Set the *experimental design* using the parameters below. This is what scientists can control. 

```{r}
numericInput('n', 'Sample size (per group)', 5)
numericInput('N', 'Number of replications', 200)
```

The parameters below determine the properties of the *population* (curly- and straight-haired people).  Scientists *don't* control these. 

The true, population-level difference in mean height (curly - straight) is 
**`r renderText(input$curly_mean - input$straight_mean)` cm**. 

```{r}
numericInput('curly_mean', 'curly_mean', 165)
numericInput('straight_mean', 'straight_mean', 160)
numericInput('curly_sd', 'curly_sd', 7)
numericInput('straight_sd', 'straight_sd', 7)
```


# One Study #

```{r}
actionButton('go_one', 'Run one study')
```

```{r}
one_study = eventReactive(input$go_one, 
                          draw_a_sample(input$n,
                                        input$curly_mean, 
                                        input$curly_sd,
                                        input$straight_mean,
                                        input$straight_sd))
# renderTable(one_study())
# renderPlotly(ggplotly(plot_a_sample(one_study())))
```

Values {data-width=200}
-----

```{r}
p_value = reactive(calculate_p_value(one_study()))
# renderText(p_value())
```

The p-value of the difference in mean heights is `r renderText(p_value())`. 

This difference **`r renderText(ifelse(p_value() < .05, 'is', 'is not'))`** statistically significant. 

```{r}
renderTable(one_study())
```

Plot {data-width=400}
-----
```{r}
renderPlotly(ggplotly(plot_a_sample(one_study()), 
                      height = plot_height, 
                      width = plot_width))
```

Padding {data-width=100}
-----



# Many Replications #

```{r}
actionButton('go_replications', 'Run many replications')
```

```{r}
replications = eventReactive(input$go_replications, 
                             replicate_N_times(input$N, 
                                               input$n,
                                               alpha = .05,
                                               input$curly_mean, 
                                               input$curly_sd,
                                               input$straight_mean,
                                               input$straight_sd))
```

Plots {.tabset data-width=900}
-----

### Plot the first replication
```{r}
##<!-- plot_a_sample(replications$sample[[1]]) -->
renderPlotly(ggplotly(plot_a_sample(replications()$sample[[1]]), 
                      height = plot_height,
                      width = plot_width))
```

### Distribution of "curly greater"
<!-- curly_greater_plot(replications) -->
```{r}
renderPlotly(ggplotly(curly_greater_plot(replications()), 
                      height = plot_height,
                      width = plot_width))
```

### Distribution of statistical significance
<!-- stat_sig_plot(replications) -->
```{r}
renderPlotly(ggplotly(stat_sig_plot(replications()), 
                      height = plot_height,
                      width = plot_width))
```

### Distribution of p-values
<!-- p_value_plot(replications) -->
```{r}
renderPlotly(ggplotly(p_value_plot(replications()), 
                      height = plot_height,
                      width = plot_width))
```

### Volcano plot {data-padding=40}
```{r}
checkboxInput('pub_bias', 'Publication bias')
```

```{r}
renderPlotly(ggplotly(volcano_plot(replications(), 
                                   publication_bias = input$pub_bias), 
                      height = plot_height,
                      width = plot_width)) 
```

Padding {data-width=100}
-----



# Power #

Power tabs {.tabset}
----

### Just numbers ###

**True power**

In statistics, *power* is the probability of getting a statistically significant outcome in a single study, *assuming a certain difference between the groups*.  Usually we assume that this difference is not 0, i.e., that the null hypothesis is false. 

```{r}
power = reactive(power.t.test(n = input$n, 
                              delta = input$curly_mean - input$straight_mean, 
                              sd = sqrt(.5 * (input$curly_sd^2 + input$straight_sd^2))))
```

Using the true difference of `r renderText(input$curly_mean - input$straight_mean)` cm, the true power is **`r renderText(str_c(round(power()$power * 100, digits = 0), '%'))`**. 

**Hypothetical power**

```{r}
numericInput('hyp_difference', 'Hypothetical difference',
             value = 5 #renderText(input$curly_mean - input$straight_mean)
)

hyp_power = reactive(power.t.test(n = input$n,
                                  delta = input$hyp_difference,
                                  sd = sqrt(.5 * (input$curly_sd^2 + input$straight_sd^2))))
```

We can also calculate power using a hypothetical or assumed difference.  In other words, what would the power be if the difference between groups were ...?  

Using the hypothetical difference of `r renderText(input$hyp_difference)` cm from the box above, the power is **`r renderText(str_c(round(hyp_power()$power * 100, digits = 0), '%'))`**. 

**Ways to increase power**

- A larger real difference between groups leads to greater power.  (Though researchers usually can't control the size of the difference.)
- A larger sample size leads to greater power.  
- A lower alpha (raising the threshold for statistical significance) leads to greater power.  

### Power and sample size ###

Power increases with sample size.  This plot uses the true difference between groups.  

```{r}
## N required for 80% power
n_req = reactive(power.t.test(delta = input$curly_mean - input$straight_mean, 
                              sd = sqrt(.5 * (input$curly_sd^2 + input$straight_sd^2)), 
                              power = .8)$n)

power_df = reactive({
    tibble(n = 2:round(1.25*n_req())) %>% 
        mutate(power = map_dbl(n, power_fn, 
                               input$curly_mean - input$straight_mean, 
                               sqrt(.5 * (input$curly_sd^2 + input$straight_sd^2))))
})

# renderTable(power_df())
renderPlotly(ggplotly(
    ggplot(power_df(), aes(n, power)) +
        geom_line() +
        geom_hline(yintercept = .80, 
                   linetype = 'dashed') +
        scale_y_continuous(labels = scales::percent_format()), 
    height = plot_height,
    width = plot_width
))
```
